---
title: "Supplementary Material 2"
subtitle: "The spatial distribution of tree-tree interaction effects on soil microbial biomass and respiration"
author: "  Henriette Christel, Simone Cesarz, Nico Eisenhauer, Georg J. A. Hähn and Rémy Beugnon"
output:
  pdf_document:
    fig_width: 20
    fig_height: 20
    fig_caption: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  
                      collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  dpi = 150)
library("tidyverse")
library("tidyr")
library("readxl")
library("lme4")
library("lmerTest")
library("performance")
library("ggiraphExtra")
library("modelr")
library("ggpubr")
library("patchwork")
library("ggeffects")
library("kableExtra")
library("corrplot")
library("dplyr")
library("ggplot2")
library("marginaleffects")
```

```{r}
#### read in data ####

transect <- read_xlsx("../01_data_transect_2019/transect_data.xlsx")

#create dataset with mono pairs only
transect2 <- transect %>% filter(species_mix != "Liqu-Sapi")

variables <- read_xlsx("../01_data_transect_2019/variable_description.xlsx")

```

## Figure S1: Correlation matrix

```{r, fig.alt= "A correlation matrix of the variables used"}
# create new numeric column for species mixture of pairs
transect$mixture <- transect$species_mix 
transect$mixture <- ifelse(transect$mixture == "Liqu-Liqu", "1",  #Liqu-Liqu mono pair = 1
                           ifelse(transect$mixture == "Sapi-Sapi", "2", "3")) #Sapi-Sapi mono pair = 2, mixture = 3
transect$mixture <- as.numeric(transect$mixture)

#### create correlation matrix of dataset (only for numeric values) ####
transect_matrix <- transect %>%
  select_if(is.numeric)
transect_matrix <- transect_matrix %>% dplyr::select(depth, root_biomass, rh, bas_res, cmic, plant_distance, close_distance, close_biomass, mixture) 

transect.corr <- cor(transect_matrix, use = 'pairwise.complete.obs') #choose pairwise complete instead of all


#### corrplot with coloured background ####
colnames(transect.corr) = c(" depth", " root biomass", " soil water content", " basal respiration", " microbial biomass", " distance to understory plants", " distance to closest tree", " biomass of closest tree", " tree pair mixture")
rownames(transect.corr) = c("depth", "root biomass", "soil water content", "basal respiration", "microbial biomass", "distance to understory plants", "distance to closest tree", "biomass of closest tree", "tree pair mixture")
coloured.corr <- corrplot(transect.corr, method="color",  
                          type = "lower", order = "original", 
                          addCoef.col = "black", # Add coefficient of correlation
                          tl.col = "black", tl.srt = 45, number.cex = 2.5, tl.cex = 2.5, #Text label color and rotation
                          col = COL2('BrBG', 10), #color scheme 
                          sig.level = 0.01, insig = "blank", # hide correlation coefficient on the principal diagonal
                          diag = FALSE)
```

\newpage

## Section S2: Microbial respiration (H1)

### Model summary

lmer(formula = bas_res ~ close_distance * depth   + (1|plot), data = df)

```{r}
mod <- lmer(formula = bas_res ~ close_distance * depth   + (1|plot), data = transect2)
summary(mod)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
p <- check_model(mod)

pp <- plot(p) 

for(i in 1:7){
pp[[i]] <- pp[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
pp
```


\newpage

## Section S3: Microbial biomass (H1)

### Model summary

lmer(formula = cmic ~ close_distance * depth   + (1|plot), data = df)

```{r}
mod1 <- lmer(formula = cmic ~ close_distance * depth   + (1|plot), data = transect2)
summary(mod1)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
q <- check_model(mod1)

qq <- plot(q) 

for(i in 1:7){
qq[[i]] <- qq[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
qq
```

\newpage

```{r, include=FALSE}
over.out <- readRDS("../01_data_transect_2019/transect_over.RDS")
```

## Section S4: Overyielding microbial respiration (H2)

### Model summary

lmer(bas_over ~ depth   + (1|plot), data = df)

```{r}
bas.depth <- lmer(bas_over ~ depth   + (1|plot), data = over.out)
summary(bas.depth)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Figure 3 Tukey test - depth

```{r}
tukey.bas <- aov(bas_over ~ depth  %>% as.factor, over.out)
summary(tukey.bas)[[1]] %>%
  as.data.frame() %>% 
  dplyr::select(-Df) %>% 
  `colnames<-`(c("Sum Sq.", "Mean Sq.", "f-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```


```{r}
TukeyHSD(tukey.bas, conf.level=.95)[[1]] %>% 
   as.data.frame() %>% 
   `colnames<-`(c("Diff", "Lower", "Upper", "p-value")) %>% 
   kbl() %>% 
   kable_paper() %>% 
   kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
b <- check_model(bas.depth)

bb <- plot(b) 

for(i in 1:6){
bb[[i]] <- bb[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
bb
```

\newpage
## Section S5: Overyielding microbial biomass (H2)

### Model summary

lmer(cmic_over ~ depth   + (1|plot), data = df)

```{r}
cmic.depth <- lmer(cmic_over ~ depth   + (1|plot), data = over.out)
summary(cmic.depth)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Figure 3 Tukey test - depth

```{r}
tukey.cmic <- aov(cmic_over ~ depth %>% as.factor, over.out)
summary(tukey.cmic)[[1]] %>%
  as.data.frame() %>% 
  dplyr::select(-Df) %>% 
  `colnames<-`(c("Sum Sq.", "Mean Sq.", "f-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```


```{r}
TukeyHSD(tukey.cmic, conf.level=.95)[[1]] %>% 
   as.data.frame() %>% 
   `colnames<-`(c("Diff", "Lower", "Upper", "p-value")) %>% 
   kbl() %>% 
   kable_paper() %>% 
   kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
C <- check_model(cmic.depth)

CC <- plot(C) 

for(i in 1:6){
CC[[i]] <- CC[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
CC
```

\newpage

## Section S6: Spatial distribution of microbial respiration overyielding (H3)

### Model summary

lmer(bas_over ~ dist.T1.center * depth   + (1|plot), data = df)

```{r}
bas.dist.depth <- lmer(bas_over ~ dist.T1.center * depth   + (1|plot), data = over.out)
summary(bas.dist.depth)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
C <- check_model(bas.dist.depth)

CC <- plot(C) 

for(i in 1:7){
CC[[i]] <- CC[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
CC
```

\newpage

## Section S7: Spatial distribution of microbial biomass overyielding (H3)

### Model summary

lmer(cmic_over ~ dist.T1.center * depth   + (1|plot), data = df)

```{r}
cmic.dist.depth <- lmer(cmic_over ~ dist.T1.center * depth   + (1|plot), data = over.out)
summary(cmic.dist.depth)$coefficients %>% 
  as.data.frame() %>% 
  dplyr::select(-df) %>% 
  `colnames<-`(c("Estimate", "Std. Error", "t-value", "p-value")) %>% 
  kbl() %>% 
  kable_paper() %>% 
  kable_styling(latex_options = "HOLD_position") 
```

### Model fit

```{r, include=FALSE}
C <- check_model(cmic.dist.depth)

CC <- plot(C) 

for(i in 1:7){
CC[[i]] <- CC[[i]] + ggplot2::theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))
}
```

```{r}
CC
```

\newpage

## Figure S2: Abiotic and biotic drivers of soil microbial biomass and respiration
```{r, include=FALSE}
tree_bio_br <- ggplot(data = transect, aes(x = close_biomass * 1000, y = bas_res, col = close_species)) +
  geom_smooth(data= transect, aes(x=close_biomass*1000, y= bas_res), method = 'lm', alpha = 0.2) +
  geom_point(aes(color = close_species)) +
  theme_bw() +
  theme(legend.position = "right")+
  theme(plot.background = element_rect(fill = "linen", colour = "linen")) +
  labs( x = "Tree biomass [kg carbon]", y = "", color = "Closest tree", fill = "Closest tree") +
  scale_color_manual(values = c("#6B3074", "#B4CF68"), labels = c(expression(italic("L. formosana")), 
                                                                  expression(italic("S. mukorossi")))) +
                       theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

# hier muss noch irgendwie die Legende drüber ohne das Bild kleiner zu machen

tree_bio_cmic <- ggplot(data = transect, aes(x = close_biomass * 1000, y = cmic, col = close_species)) +
  geom_smooth(data= transect, aes(x=close_biomass*1000, y= cmic, col = close_species), method = 'lm', alpha = 0.2, lty = 2) +
  geom_point(aes(color = close_species)) +
  theme_bw() +
  theme(legend.position = "right") +
  labs(x = "Tree biomass [kg carbon]", y = "", 
       color = "Closest tree", fill = "Closest tree") +
  scale_color_grey(start = 0.3, end = 0.7, labels = c(expression(italic("L. formosana")), 
                                                      expression(italic("S. mukorossi")))) +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

# hier muss noch irgendwie die Legende drüber ohne das Bild kleiner zu machen

#CMIC/BR ~ root biomass 
root_fig_br <- ggplot(transect) + 
  geom_point(aes(x = root_biomass, y = bas_res)) +
  theme_bw() +
  theme(plot.background = element_rect(fill = "linen", colour = "linen")) +
  labs(x = "Root biomass [g]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))


root_fig_cmic <- ggplot(transect) + 
  geom_point(aes(x = root_biomass, y = cmic)) +
  theme_bw() +
  labs(x = "Root biomass [g]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

#CMIC/BR ~ plant distance 
plant_fig_br <- ggplot(transect) + 
  geom_point(aes(x = plant_distance, y = bas_res)) +
  theme_bw() +
  theme(plot.background = element_rect(fill = "linen", colour = "linen")) +
  labs(x = "Distance to understory plants [cm]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

plant_fig_cmic <- ggplot(transect) + 
  geom_point(aes(x = plant_distance, y = cmic)) +
  theme_bw() +
  labs(x = "Distance to understory plants [cm]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

#CMIC/BR ~ relative humidity 

rh.bas <- lmer(formula = bas_res ~ rh + (1|plot), data = transect)
rh.cmic <- lmer(formula = cmic ~ rh + (1|plot), data = transect)
  
  
rh_fig_br <- ggplot(transect) + 
  geom_point(aes(x = rh, y = bas_res)) +
  geom_line(data = ggpredict(rh.bas, type = "fe") %>% as.data.frame(), 
            aes(y = rh.predicted, x = rh.x),
            color = "cornflowerblue", linewidth = 1) +
  geom_ribbon(data = ggpredict(rh.bas, type = "fe") %>% as.data.frame(), 
              aes(ymin =  rh.conf.low, ymax =  rh.conf.high, x = rh.x),
              fill = "cornflowerblue", alpha = 0.1, linewidth = 1) +
  theme_bw() +
  theme(plot.background = element_rect(fill = "linen", colour = "linen")) +
  labs(x = "Relative soil water content [%]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))


rh_fig_cmic <- ggplot(transect) + 
  geom_point(aes(x = rh, y = cmic)) +
  geom_line(data = ggpredict(rh.cmic, type = "fe") %>% as.data.frame(), 
            aes(y = rh.predicted, x = rh.x),
            color = "cornflowerblue", linewidth = 1) +
  geom_ribbon(data = ggpredict(rh.cmic, type = "fe") %>% as.data.frame(), 
              aes(ymin =  rh.conf.low, ymax =  rh.conf.high, x = rh.x),
              fill = "cornflowerblue", alpha = 0.1, linewidth = 1) +
  theme_bw() +
  labs(x= "Relative soil water content [%]", y = "") +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))

#BR ~ CMIC

mod.bas.cmic <- lmer(bas_res ~ cmic + (1|plot), transect)

brcmic_fig <- ggplot(transect) + 
  geom_point(aes(x = cmic, y = bas_res)) +
  geom_line(data = ggpredict(mod.bas.cmic, type = "fe") %>% as.data.frame(), 
            aes(y = cmic.predicted, x = cmic.x),
            color = "darkblue", linewidth = 1) +
  geom_ribbon(data = ggpredict(mod.bas.cmic, type = "fe") %>% as.data.frame(), 
              aes(ymin =  cmic.conf.low, ymax =  cmic.conf.high, x = cmic.x),
              fill = "darkblue", alpha = 0.1, linewidth = 1) +
  labs(x= expression(atop(Microbial~biomass~"["*µg~Cmic~g^{-1}~dry~soil*"]")) , 
       y = expression(atop(Microbial~respiration,"["*µl~O[2]~h^{-1}~g^{-1}~dry~soil*"]"))) +
  theme_bw() +
  theme(plot.background = element_rect(colour = "black")) +
  theme(plot.title = element_text(size = 30),
                                    plot.subtitle = element_text(size = 20),
                                    axis.title = element_text(size = 25),
                                    legend.text = element_text(size = 15))


# arranging figures and adding common y-axis title
cmic_graphics <- ggarrange(tree_bio_cmic, root_fig_cmic, plant_fig_cmic, rh_fig_cmic, 
                           ncol = 1, nrow = 4, 
                           labels = c("A", "C", "E", "G")) 

cmic_graphic <- annotate_figure(cmic_graphics, left = text_grob(expression(atop(Microbial~biomass~"["*µg~Cmic~g^{-1}~dry~soil*"]")), 
                                                                rot = 90, vjust = 1, size = 25)) +
  theme(plot.background = element_rect(fill = "white", colour = "white"))



basal_graphics <- ggarrange(tree_bio_br, root_fig_br, plant_fig_br, rh_fig_br, 
                            ncol = 1, nrow = 4, 
                            labels = c("B", "D", "F", "H"))

basal_graphic <- annotate_figure(basal_graphics, left = text_grob(expression(atop(Microbial~respiration~"["*µl~O[2]~h^{-1}~g^{-1}~dry~soil*"]")), 
                                                                  rot = 90, vjust = 1, size = 25)) +
  theme(plot.background = element_rect(fill = "linen", colour = "linen"))


#### combining graphics and saving side figures ####
side_graphics <- ggarrange(ggarrange(cmic_graphic, basal_graphic, ncol = 2),
                           brcmic_fig, labels = c("", "I") , nrow = 2, heights = c(4,2))
```

```{r}
side_graphics
```

